Time Stretching of the GeV Emission of GRBs: Fermi LAT data vs geometrical model \\ {\large \url{https://github.com/maxitg/GammaRays}}

### 2014-09-01 Paper/gammaRays.tex
Changed summary from bullet list to text

	The main results of our study may be summarized as following:
	\begin{enumerate}
		\item{
			Time stretching of GRB light curves between different VHE bands is discovered with statistical significance of $3.3\sigma$.
		}
		\item{
			This time stretching can be explained by geometry of the jet, without introducing any new spectral components.
		}
		\item{
			All GRBs can be assumed to be the same in their rest frames.
			There is no need to vary internal burst parameters.
		}
	\end{enumerate}

	There are, however, directions for improvement:
	\begin{itemize}
		\item{
			The model prediction and observations on fig. \ref{fig:correlations} are, though close, not exactly agree.
		}
		\item{
			Shapes of light curves produced by the model differ considerably from observed ones.
		}
		\item{
			Assumption of energy dependence on off-axis angle should be justified better.
		}
		\item{
			While we believe that all bursts are almost the same in their rest frames, they are certainly not exactly the same.
			The minor differences between GRBs might be responsible for observable deviations from the model predictions.
		}
	\end{itemize}

	We believe, however, that these problems are not unresolvable, and may be addressed by refining the model without changing its main assumptions.

>>>>

	Our study can be summarized with 3 main conclusions.

	First, the time stretching of GRB light curves between different VHE (in particular $(\unit[100]{MeV}, \unit[1]{GeV})$ and $(\unit[1]{GeV}, \unit[300]{GeV})$) bands is discovered with statistic significance of $3.3\sigma$.
	This time stretching might be positive or negative (that is higher or lower energy light curve is stretched) depending on the burst.

	Second, this time stretching effect can be explained with curvature effects, that is effects of jet geometry.
	There is no need to introduce any new spectral components.

	Finally, we can assume all GRBs to be the same in their rest frames.
	The internal burst parameters (such as $\gamma$, $\eta_0$, $r_0$, $n$, $\omega_0$, $\theta_0$, $k$ and $\alpha$) might stay the same for all bursts, and this assumption is more or less consistent with existing observations.

	However, there are some caveats, and directions for improvement.

	First of all, the model prediction and observations are not completely consistent.
	If you look at fig. \ref{fig:correlations}, you will see that the stretching factor of GRB 090926A is too high compared to the model prediction.
	It appears that parameters of the model cannot be fitted to account for it (without ruining agreement with other observations).
	More data should be analyzed to see whether the problem will be exacerbated, and some refinement of the model might also be required.

	Second, the shapes of light curves produced by the model (see fig. \ref{fig:sampleLightCurves}) differ considerably from observed ones (e.g. fig. \ref{fig:grb090902B}).
	Most importantly, the slope of light curves produced by the model is zero at $t = 0$, even though the slope of observed light curves at $t = 0$ is not only non-zero, but appears to have a maximum.

	Third, the assumption of plasma energy dependence on off-axis angle should be better justified.
	This might probably be done using hydrodynamic simulation of the jet.

	Finally, even though it appears that bursts are similar in their rest frames, they cannot be exactly the same.
	The differences in masses, metallicities, angular momenta of progenitor stars, and the differences in local conditions around them might account for differences in light curves of GRBs (or, even, for especially large stretching factor of GRB 090926A).
	It means that minor variations of model parameters might be necessary on burst per burst basis.

	It seems, however, that all these problems are not unresolvable, and may be addressed by refining the model without changing its main assumptions.
